%% Based on a TeXnicCenter-Template by Gyorgy SZEIDL.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%------------------------------------------------------------
%
\documentclass[12pt]{article}%
%Options -- Point size:  10pt (default), 11pt, 12pt
%        -- Paper size:  letterpaper (default), a4paper, a5paper, b5paper
%                        legalpaper, executivepaper
%        -- Orientation  (portrait is the default)
%                        landscape
%        -- Print size:  oneside (default), twoside
%        -- Quality      final(default), draft
%        -- Title page   notitlepage, titlepage(default)
%        -- Columns      onecolumn(default), twocolumn
%        -- Equation numbering (equation numbers on the right is the default)
%                        leqno
%        -- Displayed equations (centered is the default)
%                        fleqn (equations start at the same distance from the right side)
%        -- Open bibliography style (closed is the default)
%                        openbib
% For instance the command
%           \documentclass[a4paper,12pt,leqno]{article}
% ensures that the paper size is a4, the fonts are typeset at the size 12p
% and the equation numbers are on the left side
%

\usepackage{url}

\begin{document}

\title{The Eureka Society \\ Membership Application Form}
\maketitle

\tableofcontents


\section{Application}

\begin{description}
	\item[NAME] Brannon, Terrence Monroe 
	\item[ADDRESS] 506 Bridgeford Dr.
	\item[CITY, STATE, ZIP, COUNTRY] Westerville, OH 43081, USA
	\item[HOME PHONE / WORK PHONE] 818-359-0893 / 818-359-0893
	\item[CELL PHONE / FAX NUMBER] 818-359-0893 / unknown
	\item[EMAIL] metaperl.santmat@gmail.com
	\item[DATE OF BIRTH / BIRTHPLACE] May 11, 1969 / Columbia, SC, USA
	\item[GENDER / MARRIED OR SINGLE / NO. OF CHILDREN] Male, Single, no children
	\item[OCCUPATION] - Computer Programmer / Data Analyst
	\item[ANY PETS?  IF SO, WHAT KIND(S)?] no pets
	\item[HAVE YOU MEDITATED BEFORE?  IF SO, WHAT TYPE(S)?] Please see Section \ref{sec:med}
	\item[IF SO, BRIEFLY DESCRIBE THE TECHNIQUES] Please see Section \ref{sec:med}
	\item[HOW DID YOU HEAR ABOUT THE EUREKA SOCIETY?] I was doing a comprehensive web search for a Sant Mat Lineage to follow when I ran across your Yahoogroup.
	\item[ARE YOU TAKING MEDICATIONS?  IF SO, WHICH ONE(S)?] no medications.
	\item[HAVE YOU EVER BEEN HYPNOTIZED?] Yes, once I was a student at the American Institute for Hypnotherapy in Southern California. During a practice session, a lady hypnotized me and brought me out. I was not there for long though.
	\item[HAVE YOU EVER BEEN A MEDIUM?] no
	\item[HAVE YOU EVER CHANNELED?] no
	\item[WHAT ARE YOUR SPIRITUAL ASPIRATIONS?]  Please see Section \ref{sec:asp}
	\item[WHAT SPARKED YOUR INTEREST IN JOINING THE EUREKA SOCIETY?] The main thing which interested me is the ability to get involved with sound current work without the guru-chela relationship. Also, I carefully read the Yahoogroup archive messages and was impressed with the results that students of the system were getting. Also, when David Christopher Lane attempted to enter the group and debunk Audinometry, I like how Jennifer openly invited David to try a harmonic device session. This is in contrast to the typical defensive, angry hateful response I often see in this situation. I also like the payment arrangements. The arguments about karma load and money make sense. I also like the development of a protocol to validate inner experience. I like having teachers who speak English natively. I also like the open-ness of the application process. I don't feel like I'm being scrutinized and forced into a certain mold. Most importantly this is a results-oriented evolving system based on trial and error instead of a do-what-I-because-this-is-holy-and-perfect system. Also, I salute the attitude towards sexuality.
	
	 
	
\end{description}

\section{Meditations: Types and Techniques}
\label{sec:med}

The attached resume pretty much covers this question, but I will do my best to give some details here in reverse chronological order. I will list the systems that I put a lot of time and/or energy into.

\subsection{Natural Meditation (7/2007)}

Natural meditation, \url{http://naturalmeditation.net/}, is an ultra-passive system. You just down and anything that happens to the body or the mind, you acknowledge that the Creator is doing it not you. Over time, you end up stretching the body and going into more and more advanced yoga poses as the Creator continues his molding of you to his liking. I only did this for about 2 weeks, but I really liked it.

\subsection{Falun Gong (6/2007 and 2 weeks in the year 2000)}

I recently did some Falun Gong, \url{http://www.falundafa.org/}, and also did some back in 2000. Again, not for more than 2 weeks total. Falun Gong is a series of 5 exercises labeled as ``Qi Gong of the Buddha School'' --- in other words, it has no relation to the Buddhist religion and it has no relation to other Qi Gongs. Other Qi Gongs (Chi Kungs) cultivate a certain elixir. This one builds a substance called Gong. 4 of the poses are standing and the 5th one is sitting. It leads to great tranquility and supernatural powers.

Master Li Hongzhi (the founder) talks freely about magic, the Bermuda Triangle and other powers. It is quite an effective system. The main reason I quit doing it was it required will to hold the postures and I found it much easier to sit back and focus at the 3rd eye and wait for the Master Power to take me away.

\subsection{Silva Ultramind (4/2007) }

Silva Ultramind, \url{http://en.wikipedia.org/wiki/Silva_Method}, involved listening to a tone designed to take your brain into the alpha frequency, where brain waves go when one meditates. I did this for about 4-6 weeks. Near the end, I was having these camera-like flashes of awareness, where instead of looking and evaluating my perceptive apparatus turned into a passionless directly aware movie camera. I couldn't tell you why I stopped doing this. It was a nice system.

\subsection{Advaita Vedanta (12/2005 - 3/2007)}

I studied Advaita Vedanta with AHAM, \url{http://www.AHAM.com}. This is a lineage based around the teachings of Ramana Maharishi. It primarily involved paying attention to the sense of I AM so that the little self could be replaced with Self-realization. Their response to sound current work would be: ``who is the one listening to the sound current?'' Their attempts to destroy the ego can be summed up in a statement by their spiritual director, Arunachala Ramana: ``Enlightenment is freedom from being an individual, not having the freedom of being an individual.'' Of course, the right-hand path of The Eureka Society completely disagrees with this.

\subsection{Dianetics and Scientology - (12/2006 - 3/2007)}

Received auditing from the Tampa Church of Scientology. Auditing is a process where you relate a traumatic incident over and over, each time attempting to pick up more sensory data about the incident. In the process, the incident becomes just another series of pictures in your mind instead of something you react to with fear, anger or other counter-productive emotions. Had approximately 12 private auditing sessions over a 3-month period. I left the Church because I found them very controlling. I also left because I saw firsthand how the writings of L. Ron Hubbard had been altered by the Church. 

\subsection{Pranayama (2005)}

Studied with a monk from the Self-Realization Fellowship named Sankara Saranam, \url{http://www.pranayama.org/}. Performed a variety of body locks, inhales, and holds of breath while keeping physical eyes pointed at third eye.

\subsection{Buddhist Meditation}

\begin{description}
	\item[11/2001 - 12/2001] 31-day insight meditation retreat. Paid attention to each of the senses. Watched the rise and fall of my stomach. I got to the point of where my thoughts just went flying by without me reacting to them. 
	\item[1999] SN Goenka insight meditation retreat. Again paid attention to bodily sensations. Spent 7 days there. Could not speak the whole time.
	 \item[1998] Zen center of Los Angeles. Lived here and practiced Zen Meditation - focusing on the wall in front and counting the breaths. Did this for about 4-5 months.
 
\end{description}

\subsection{Brainwave Audio Meditation}

\begin{description}
	\item[Monroe Institute] bought several of their cd packs.Never quite got out of body. My chess game improved when I listened to their alpha cds while playing.
	\item[Centerpointe Institute] this system was very good at turning you into a waiter. A watcher. A listener. I had some extremely profound instances of dropping all expectation and simply watching.
	\item[Synchronicity Institute] used this system for about 2-4 weeks. On the very first night, I put on the CD and had a nice meditation. Then the people next door got loud. I decided to ask my self ``who is getting angry at them?'' and before I knew it, my body had liquified and extended across to the wall next to the people next door.
	\item[Life Technology] These people, \url{http://www.lifetechnology.org/}, make a wide range of devices. Their astral project CD was good. I then bought the Time Traveler CD. But when I put it in, it was recognized as being the astral project CD. When I asked the owners about this, they said the CDs were similar. I think he was lying. I requested my money back and dont want to buy anything else from
	\item[Inlakesh] This musical duo out of New Mexico, \url{http://www.inlakesh.com/}, produces some amazingly powerful shamanic journeying trance music. Their CD, ``The Gathering'' was amazing. Like everything else I have tried, I used it many times. But sporadically over many years. Just when I felt like it.
\end{description}

\subsection{Heavenly Circuit Qi Gong (1994)}

In this meditation you draw energy up the spine on the inhale and down the front of the body on the exhale. When doing this meditation right before bed, I would many times have dreams of controlling the ability to fly at will. These were fairly long dreams. At other times, I found myself hurtling through deep space at a very fast speed. I was screaming in bed while this was happening.

\subsection{Sahaj Marg (1992)}

Sahaj Marg is a pranic transmission meditation. You simply sit down in front of the other person. And then you think ``there is Divine Light in my heart''. This usually leads to you falling unconscious for the length of the session while the person transmits prana into your heart.

\section{Spiritual Aspirations}
\label{sec:asp}

I have been wandering quite a bit for many years spiritually. I always have liked Ambient and Space Music. I was always interested in Astral Travel. I really just want to know what exists and what is real. In other words, my 5 senses are telling me that only this plane is real. But are all the mystics just blowing smoke? What about UFOs and aliens? I'd like to meet some. I need to find these things out to create meaning in my life. Without understanding, I cannot be happy and satisfied. I want control over myself. I am a bundle of tension and reflexes.

Basically, I have never found a system which seemed to stick. They all lacked in one way or the other. I found certain people intimidating. Others manipulative. Other systems were impotent. Others were non-comprehensive. Some were not fun. I want to know how the whole game works. I want to hear the Cosmic Symphony.

Also, I want to appreciate everyone for where they are spiritually instead of being a snob or elitist.


\end{document}
